---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Github APIv3 (REST)

```{r}
library(jsonlite)
library(httpuv)
library(httr)
library(gh)

token <- Sys.getenv("GH_CLIENT_SECRET")
if (token == '') {
  stop('You need a github token', call. = FALSE)
}
```

The Github REST API v3 lists everything as `curl` commands,
so when they say something like:

```{bash}
curl https://api.github.com/zen
```

You can make the equlivalent call from the `gh` package:

```{r}
gh::gh("https://api.github.com/zen")
```

You can pass in the raw GET command

```{r}
gh("https://api.github.com/users/chendaniely")
```

Or create "variables" that you can pass in using the `:` in the GET command,
this comes in handy when you start working wiht the various endpoints.

```{r}
gh("https://api.github.com/users/:user", user = 'chendaniely')
```

For example, the endpoint for listing organization repositories

```
GET /orgs/:org/repos
```

Can be passed into the `gh` function as well

```{r}
gh("/repos/:owner/:repo/contributors", owner = 'numpy', repo = 'numpy')
```


